\documentclass[a4paper,twoside,11pt]{article}
\usepackage{a4wide,graphicx,fancyhdr,amsmath,amssymb,float,wrapfig}
\usepackage[bottom]{footmisc} % Make footnotes stick to the bottom of a page
\usepackage{hyperref}


%----------------------- Macros and Definitions --------------------------

%\setlength\headheight{20pt}
\addtolength\topmargin{0pt}
%\addtolength\footskip{20pt}

\fancypagestyle{plain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-------------------------------- Title ----------------------------------

\title{}
\date{}

%--------------------------------- Text ----------------------------------

\begin{document}

%\maketitle

\begin{center}
\Huge{Minutes First Meeting Group 14}
\\\vspace*{2mm}
\Large{April 26 2017, 17:00}
\\\vspace*{2mm}
\large{MF 5.146}
\\
		\end{center}

		\textbf{Present:} \textit{M. de Brouwer} (secretary), \textit{S. Marin} (president)
\\\indent\qquad\,\,\,\,\,\qquad\quad \textit {A. Wemmenhove, M. Struijs (tutor), J.W.L. Savelsberg}

		\textbf{Absent:} \textit{B. Floris (Notified us)}
		
	\section{Opening}
	
	The meeting opened at 17:03. \\
	Job arrived at 17:04

	\section{Do we need to send the minutes afterwards?}
	
	Minutes need to be mailed by the end of the week to the tutor. \\
	We wil decide later whether or not we will do 2 meetings a week. 
	
	\section{Planning}
	
	Formatting of the planning is irrelevant. We should mention what needs to be done and by who and when. Try to be as specific as possible. Make people responsible for certain deliverables to make planning easier. 
	
	\section{Submission of the algorithm}
	
	We won't be provided any test cases, we need to make them ourselves. 
	
	\section{Final inquiry}
	
	We have set up overleaf, github and google drive already. We have also made a bruteforce algorithm. We have found some algorithms online, try to make sure these come from published papers. For the prototype it is only important that input is read correctly and output is given correctly. \\
	The deadline of the weekly logbook is every sunday. You have to upload it to canvas. If no spot appears on canvas you have to upload to the files under your group. 
	
	\section{Next meeting}
	
	The tutor is only available for the 7th and 8th hour on wednesday. Our next meeting will be scheduled for the 3rd of May at 17:00 to at most 17:30. 
	\\\\
	Meeting closed 17:14

	\end{document} 
