\documentclass[a4paper,twoside,11pt]{article}
\usepackage{a4wide,graphicx,fancyhdr,amsmath,amssymb,float,wrapfig}
\usepackage[export]{adjustbox}

%----------------------- Macros and Definitions --------------------------

%\setlength\headheight{20pt}
\addtolength\topmargin{0pt}
%\addtolength\footskip{20pt} 
\fancypagestyle{plain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-------------------------------- Title ----------------------------------

\title{}
\date{}

%--------------------------------- Text ----------------------------------

\begin{document}

%\maketitle

\begin{center}
	\Huge{Minutes Seventh Meeting Group 14}
	\\\vspace*{2mm}
	\Large{June 14 2017, 4:15PM}
	\\\vspace*{2mm}
	\large{MF 5.146}
	\\
\end{center}

\textbf{Attendees:} \textit{M. de Brouwer} (secretary),
\textit{B. Floris}, \textit{S. Marin} (president)
\\\indent\qquad\,\,\,\,\,\qquad\quad \textit{J. Savelsberg, A. Wemmenhove, M. Struijs} (tutor)

\section{Opening}
\subsection{General remarks}
Jelle wants to talk about testing

\section{State of the algorithms}
Mike and Jelle have worked on the optimal algorithm. The optimal algorithm has been improved, in the next 3 days they will work on improving the pruning and adding dominance pruning. We have tested on several different inputs, on smaller rectangles it works great for even 10 rectangles but making the rectangles bigger gives timing issues at the moment. By saturday we plan to have the optimal algorithm done. 

\noindent Bogdan is gonna work on the binary tree algorithm to implement a randomizer.
\subsection{Submission of the algorithm}
We want to have everything done by saturday so we have 3 days to implement timing and go through everything. 

\section{Testing}
We are currently doing tests but it would be best to wait until we have the algorithm finished so we do not have to redo the tests. Might be an idea to automate the tests to make it go quicker. 

\noindent Try to keep everyone updated if there are edge cases in the tests. \\
TODO Sergiu: add what algorithm was used to the debug file.\\

\section{Report}
It is fine to work on the report when you have time, if you are busy with exams do your part before the exam week. \\

\section{Planning}
Sergiu won't be available for the last week before the report deadline. \\
Thursday the 6th of July is when we want the report to be finished. \\
Next week there will be presentations, we will do a quick informal meeting after the presentations to discuss the progress on the report. Martijn thinks this will be fine but he will think about this.  

\section{Final Remarks}

\section{Closing}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
