\documentclass[a4paper,twoside,11pt]{article}
\usepackage{a4wide,graphicx,fancyhdr,amsmath,amssymb,float,wrapfig}
\usepackage[bottom]{footmisc} % Make footnotes stick to the bottom of a page
\usepackage{hyperref}
\usepackage{lineno}


%----------------------- Macros and Definitions --------------------------

%\setlength\headheight{20pt}
\addtolength\topmargin{0pt}
%\addtolength\footskip{20pt}

\fancypagestyle{plain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%
\newcommand{\ts}{\textsuperscript}


%-------------------------------- Title ----------------------------------

\title{}
\date{}

%--------------------------------- Text ----------------------------------

\begin{document}

%\maketitle



\begin{center}
	\Huge{Minutes 6\ts{th} Meeting Group 14}
	\\\vspace*{2mm}
	\Large{June 07 2017}
	\\\vspace*{2mm}
	\large{MF 5.146}
	\\
\end{center}

\textbf{Present:}  \textit{Bogdan Floris} (chairman) , \textit{Jelle Wemmenhove}, \textit{Mike de Brouwer},  
\\\indent\qquad\,\,\,\,\,\qquad\quad \textit{Sergiu Marin}(secretary), \textit{Job Savelsberg}, \textit{Martijn Struijs} (tutor)

\linenumbers
\modulolinenumbers[5]

\section{Opening}

Bogdan opens the meeting at 16:59 hour.

\subsection{General remarks}

- 

\section{Feedback Midterm Report}
\begin{itemize}
	\item Overall, the report was decent - the algorithms were interesting - the descriptions lacked and was sometimes unclear.
	\item we should label the figures - add captions.
	\item the running time for the brute force algorithm should be explained better.
	\item we should only mention the running times briefly - also a short description of how we arrived at that running time should be added
	\item introduce the terms either at the start of the algorithm or in the introduction (bin and rectangles) (it's maybe better to call them all rectangles to make the paper more consistent - this is a mathematical paper and not an essay)
\end{itemize}

\section{State of the algorithms}
\begin{itemize}
	\item BinTreeAlgorithm - now considers all the heuristics - this is done - the only thing that needs to be done is to make sure that it runs in under 5 min on a difficult test case
	\item Optimal Algorithm - the first pruning step is done - the issues were with testing - now that is being fixed - the pruning indeed makes things easier.
	\item Maximal Rectangles Algorithm - some minor optimizations are to be added
\end{itemize}

\section{Report}
For the testing part - replicate the tests from the papers - also pick samples on which the algorithm does well or super bad and explain why that happens. For the report it may be a good idea to cut the pseudocode all-together in order to save up space.

\section{Assigning Tasks}
\begin{itemize}
	\item Bogdan: experiment with the algorithm and add special test cases 
	\item Sergiu: improve the Maximal Rectangles Algorithm and rewrite the Optimal and Maximal Algorithm section in the report 
	\item Mike: add pruning and test the actual pruning
	\item Job: generate the test-cases, also start working on the report
	\item Jelle: implement improvements for optimal rectangle packing
\end{itemize}

\section{Final Remarks}
No final remarks.

\section{Closing}

Bogdan closes the meeting at 17:31.


\end{document}
